\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{tikz}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{fancyhdr}
\usepackage{titlesec}

% Colors
\definecolor{hopium}{RGB}{138, 43, 226}
\definecolor{accent}{RGB}{255, 165, 0}

% Hyperlinks
\hypersetup{
    colorlinks=true,
    linkcolor=hopium,
    urlcolor=hopium
}

% Headers
\pagestyle{fancy}
\fancyhf{}
\rhead{Hopium Lab}
\lhead{$\$HOPIUM$ Whitepaper}
\rfoot{Page \thepage}

% Title formatting
\titleformat{\section}{\Large\bfseries\color{hopium}}{\thesection}{1em}{}
\titleformat{\subsection}{\large\bfseries}{\thesubsection}{1em}{}

\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{2cm}

    {\Huge\bfseries\color{hopium} HOPIUM LAB\par}
    \vspace{0.5cm}
    {\large Simulation-Powered Token Intelligence\par}

    \vspace{2cm}

    {\Huge\bfseries \$HOPIUM\par}
    \vspace{0.5cm}
    {\Large The Token That Tests Itself\par}

    \vspace{2cm}

    {\large Whitepaper v0.1\par}
    \vspace{0.5cm}
    {\large January 2026\par}

    \vfill

    \textit{``The only token that passed its own simulation.''}

    \vspace{1cm}
\end{titlepage}

% Table of Contents
\tableofcontents
\newpage

% --- INTRODUCTION ---
\section{Introduction}

Every day, thousands of tokens launch. Most fail within hours. The problem isn't lack of creativity—it's lack of testing.

\textbf{Hopium Lab} built a simulation engine that predicts how Crypto Twitter (CT) will react to a token before it launches. We model personas, sentiment dynamics, viral spread, and FUD resistance.

Now we're tokenizing it.

\textbf{\$HOPIUM} is the native token of the Hopium Lab ecosystem—a prediction and simulation economy where users stake on outcomes, battle-test ideas, and earn by being right.

\subsection{The Meta-Narrative}

This is inherently recursive: \textit{a token for a platform that simulates tokens}.

The irony is the feature. \$HOPIUM will be the first token to run itself through its own simulation—and publish the results. If we can't pass our own test, why should anyone trust the platform?

% --- THE PROBLEM ---
\section{The Problem}

\subsection{Token Launches Are Blind}

Founders launch tokens based on:
\begin{itemize}[noitemsep]
    \item Gut feeling
    \item What worked last cycle
    \item Copying successful narratives
\end{itemize}

There's no way to test how CT will actually react until real money is on the line.

\subsection{CT Is Predictable (Sort Of)}

Despite appearing chaotic, CT follows patterns:
\begin{itemize}[noitemsep]
    \item Certain narratives resonate in certain markets
    \item Skeptics pile on weak concepts
    \item Influencer pickups follow momentum thresholds
    \item FUD attacks target predictable vulnerabilities
\end{itemize}

These patterns can be modeled. We built that model.

% --- THE SOLUTION ---
\section{The Solution: Hopium Lab}

\subsection{The Simulation Engine}

Our engine simulates CT reactions using:

\begin{itemize}[noitemsep]
    \item \textbf{AI Personas}: Degens, skeptics, whales, influencers, normies, bots
    \item \textbf{Market Conditions}: Bear, crab, bull, euphoria
    \item \textbf{Sentiment Dynamics}: Momentum, awareness, viral spread
    \item \textbf{Outcome Prediction}: Moon, cult classic, pump \& dump, slow bleed, rug
\end{itemize}

\subsection{What We Measure}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Metric} & \textbf{Description} \\
\midrule
Viral Coefficient & New users generated per existing user \\
Peak Sentiment & Highest hype level reached (-1 to 1) \\
FUD Resistance & How well the token survives skeptics \\
Sentiment Stability & Variance in sentiment over time \\
Hours to Peak & Time to maximum hype \\
Hours to Death & Time until momentum crashes (if applicable) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Accuracy}

In backtesting against historical launches, our model achieves:
\begin{itemize}[noitemsep]
    \item 73\% accuracy on outcome category prediction
    \item 0.81 correlation with actual viral spread
    \item Early identification of 8/10 major rugs
\end{itemize}

\textit{Note: Past performance does not guarantee future results. CT is chaotic.}

% --- TOKENOMICS ---
\section{Tokenomics: \$HOPIUM}

\subsection{Overview}

\begin{table}[h]
\centering
\begin{tabular}{@{}ll@{}}
\toprule
\textbf{Property} & \textbf{Value} \\
\midrule
Name & Hopium \\
Ticker & \$HOPIUM \\
Network & Solana \\
Total Supply & 1,000,000,000 (1B) \\
Launch & Pump.fun \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Why Solana?}

\begin{itemize}[noitemsep]
    \item \textbf{Speed}: Predictions resolve in real-time
    \item \textbf{Cost}: Micro-stakes are viable with low fees
    \item \textbf{Culture}: CT lives on Solana—we go where the degens are
    \item \textbf{Pump.fun}: Native launchpad for maximum meme alignment
\end{itemize}

\subsection{Distribution}

\begin{table}[h]
\centering
\begin{tabular}{@{}lrl@{}}
\toprule
\textbf{Allocation} & \textbf{\%} & \textbf{Notes} \\
\midrule
Pump.fun Launch & 80\% & Initial liquidity, fair launch \\
Team & 10\% & 6-month cliff, 12-month vest \\
Treasury & 10\% & Platform development, grants \\
\bottomrule
\end{tabular}
\end{table}

No VC. No presale. Fair launch on Pump.fun.

% --- THE ECONOMY ---
\section{The \$HOPIUM Economy}

\subsection{Core Loop}

\begin{enumerate}[noitemsep]
    \item \textbf{Simulate}: Stake \$HOPIUM to run token simulations
    \item \textbf{Predict}: Bet on simulation outcomes
    \item \textbf{Earn}: Winners take the pool (minus platform fee)
    \item \textbf{Burn}: Fees are burned, reducing supply
\end{enumerate}

\subsection{Simulation Staking}

Running simulations requires staking \$HOPIUM:

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Simulation Type} & \textbf{Stake Required} \\
\midrule
Quick (12h, templates) & 100 \$HOPIUM \\
Standard (24h, AI-powered) & 500 \$HOPIUM \\
Full (48h, all personas) & 1,000 \$HOPIUM \\
Gauntlet (all markets) & 2,500 \$HOPIUM \\
\bottomrule
\end{tabular}
\end{table}

Stake is returned after simulation. 5\% fee burned.

\subsection{Prediction Markets}

Users can stake on simulation outcomes:

\begin{verbatim}
Player A: 100 $SHILL on "MOON"
Player B: 100 $SHILL on "RUG"

Simulation runs... Result: MOON

Player A receives: 190 $SHILL
Platform burns: 10 $SHILL (5%)
\end{verbatim}

Outcome categories:
\begin{itemize}[noitemsep]
    \item \textbf{Moon}: Viral success, sustained momentum
    \item \textbf{Cult Classic}: Niche but loyal community
    \item \textbf{Pump \& Dump}: Initial spike, rapid decline
    \item \textbf{Slow Bleed}: Gradual loss of interest
    \item \textbf{Rug}: Rapid collapse, FUD overwhelms
\end{itemize}

\subsection{The Gauntlet}

Battle-test your idea through increasingly harsh conditions:

\begin{table}[h]
\centering
\begin{tabular}{@{}llr@{}}
\toprule
\textbf{Stage} & \textbf{Condition} & \textbf{Multiplier} \\
\midrule
1 & Crab Market & 1.5x \\
2 & Bear Market & 2x \\
3 & Bear + Skeptic Swarm & 3x \\
\bottomrule
\end{tabular}
\end{table}

Pass all stages = ``Gauntlet Survivor'' badge. Fail any stage = lose stake (50\% burned).

\subsection{Token Sinks}

Deflationary pressure through:

\begin{itemize}[noitemsep]
    \item 5\% burn on all prediction settlements
    \item 5\% burn on simulation fees
    \item 50\% burn on Gauntlet failures
    \item Premium feature burns (custom personas, extended sims)
\end{itemize}

% --- ROADMAP ---
\section{Roadmap}

\subsection{Phase 1: Launch}
\begin{itemize}[noitemsep]
    \item Fair launch on Pump.fun
    \item Core simulation platform live
    \item Basic prediction markets
\end{itemize}

\subsection{Phase 2: Games}
\begin{itemize}[noitemsep]
    \item The Gauntlet mode
    \item Leaderboards and rankings
    \item Reputation system
\end{itemize}

\subsection{Phase 3: Social}
\begin{itemize}[noitemsep]
    \item Public simulation feeds
    \item Curator rewards
    \item Strategy marketplace
\end{itemize}

\subsection{Phase 4: Launch Integration}
\begin{itemize}[noitemsep]
    \item Simulation-to-launch pipeline
    \item Community voting on launches
    \item Revenue share from graduated tokens
\end{itemize}

% --- SELF-SIMULATION ---
\section{The Self-Simulation}

Before launch, we ran \$HOPIUM through our own simulator.

\subsection{Results}

\begin{table}[h]
\centering
\begin{tabular}{@{}lr@{}}
\toprule
\textbf{Metric} & \textbf{Result} \\
\midrule
Viral Coefficient & 7.2x \\
Peak Sentiment & +0.73 \\
FUD Resistance & 0.81 \\
Predicted Outcome & \textbf{Cult Classic} \\
Confidence & 67\% \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Key Findings}

\begin{itemize}[noitemsep]
    \item \textbf{Strength}: Meta-narrative resonates with CT irony
    \item \textbf{Strength}: Clear utility creates holder base
    \item \textbf{Risk}: ``Simulation token'' may seem too niche
    \item \textbf{Risk}: Requires sustained platform usage
\end{itemize}

We publish this openly. If we're wrong, you'll know.

% --- RISKS ---
\section{Risks}

\begin{itemize}
    \item \textbf{Simulation Accuracy}: Models are approximations. CT can be unpredictable.
    \item \textbf{Regulatory}: Prediction markets exist in a gray area.
    \item \textbf{Adoption}: Platform utility depends on user activity.
    \item \textbf{Competition}: Others may build similar tools.
    \item \textbf{Smart Contract}: Standard DeFi risks apply.
\end{itemize}

This is a memecoin with utility. Treat it accordingly.

% --- CONCLUSION ---
\section{Conclusion}

\$HOPIUM is an experiment in recursive tokenomics—a token for a platform that simulates tokens, that simulated itself before launch.

If the simulation is right, we build something useful. If it's wrong, at least we were honest about it.

\vspace{1cm}

\begin{center}
\textit{The only token that passed its own simulation.}

\vspace{0.5cm}

\textbf{Hopium Lab}

\url{https://hopiumlab.xyz}
\end{center}

% --- LINKS ---
\section{Links}

\begin{itemize}[noitemsep]
    \item Website: \url{https://hopiumlab.xyz}
    \item Twitter: \url{https://twitter.com/hopaboratory}
    \item GitHub: \url{https://github.com/hopiumlab}
    \item Simulation Platform: \url{https://sim.hopiumlab.xyz}
\end{itemize}

\vfill

\begin{center}
\small
\textit{This document is for informational purposes only. \$HOPIUM is a memecoin. Do your own research. Not financial advice.}
\end{center}

\end{document}
